\tabulinesep=1mm
\begin{longtabu}spread 0pt [c]{*{2}{|X[-1]}|}
\hline
\PBS\centering \cellcolor{\tableheadbgcolor}\textbf{ File  }&\cellcolor{\tableheadbgcolor}\textbf{ Description   }\\\cline{1-2}
\endfirsthead
\hline
\endfoot
\hline
\PBS\centering \cellcolor{\tableheadbgcolor}\textbf{ File  }&\cellcolor{\tableheadbgcolor}\textbf{ Description   }\\\cline{1-2}
\endhead
\mbox{\hyperlink{mavtest_8py}{mavtest.\+py}}  &Demonstrates creating a mavlink message, putting it on a buffer and then decoding from said buffer.   \\\cline{1-2}
\mbox{\hyperlink{bwtest_8py}{bwtest.\+py}}  &Check bandwith of link. Display results on terminal.   \\\cline{1-2}
\mbox{\hyperlink{mav__accel_8py}{mav\+\_\+accel.\+py}}  &Show accelerometer calibration for a set of logs.   \\\cline{1-2}
\mbox{\hyperlink{apmsetrate_8py}{apmsetrate.\+py}}  &Set the Stream Rate on an A\+PM.   \\\cline{1-2}
\mbox{\hyperlink{magtest_8py}{magtest.\+py}}  &Rotate A\+P\+Ms on bench to test magnetometers.   \\\cline{1-2}
\mbox{\hyperlink{mavtcpsniff_8py}{mavtcpsniff.\+py}}  &Connect as a client to two tcpip ports on localhost with mavlink packets. Pass them both directions, and show packets in human-\/readable format on-\/screen.   \\\cline{1-2}
\mbox{\hyperlink{mav2pcap_8py}{mav2pcap.\+py}}  &Packetizes a binary M\+A\+V\+Link stream. The resulting packets are stored into a P\+C\+AP file, which is compatible to tools like Wireshark.   \\\cline{1-2}
\mbox{\hyperlink{wptogpx_8py}{wptogpx.\+py}}  &Extract G\+PS data from a waypoint file, and create a G\+PX file, for loading into Google Earth.   \\\cline{1-2}
\mbox{\hyperlink{mavgps_8py}{mavgps.\+py}}  &Allows connection of the u\+Blox u-\/\+Center software to a u\+Blox G\+PS device connected to a P\+X4 or Pixhawk device, using Mavlink\textquotesingle{}s S\+E\+R\+I\+A\+L\+\_\+\+C\+O\+N\+T\+R\+OL support to route serial traffic to/from the G\+PS, and exposing the data to u-\/\+Center via a local \mbox{\hyperlink{classTCP}{T\+CP}} connection.   \\\cline{1-2}
\mbox{\hyperlink{mavtester_8py}{mavtester.\+py}}  &Test mavlink messages.   \\\cline{1-2}
\end{longtabu}
