{\bfseries{cat}} -\/ \mbox{[}filename\mbox{]} Display file’s contents to the standard output device (usually your monitor).

{\bfseries{cd}} -\/ /directorypath Change to directory.

{\bfseries{chmod}} -\/ \mbox{[}options\mbox{]} mode filename Change a file’s permissions.

{\bfseries{chown}} -\/ \mbox{[}options\mbox{]} filename Change who owns a file.

{\bfseries{clear}} -\/ Clear a command line screen/window for a fresh start.

{\bfseries{cp}} -\/ \mbox{[}options\mbox{]} source destination Copy files and directories.

{\bfseries{date}} -\/ \mbox{[}options\mbox{]} Display or set the system date and time.

{\bfseries{df}} -\/ \mbox{[}options\mbox{]} Display used and available disk space.

{\bfseries{du}} -\/ \mbox{[}options\mbox{]} Show how much space each file takes up.

{\bfseries{file}} -\/ \mbox{[}options\mbox{]} filename Determine what type of data is within a file.

{\bfseries{find}} -\/ \mbox{[}pathname\mbox{]} \mbox{[}expression\mbox{]} Search for files matching a provided pattern.

{\bfseries{grep}} -\/ \mbox{[}options\mbox{]} pattern \mbox{[}filesname\mbox{]} Search files or output for a particular pattern.

{\bfseries{kill}} -\/ \mbox{[}options\mbox{]} pid Stop a process. If the process refuses to stop, use kill -\/9 pid.

{\bfseries{less}} -\/ \mbox{[}options\mbox{]} \mbox{[}filename\mbox{]} View the contents of a file one page at a time.

{\bfseries{ln}} -\/ \mbox{[}options\mbox{]} source \mbox{[}destination\mbox{]} Create a shortcut. locate filename Search a copy of your filesystem for the specified filename.

{\bfseries{lpr}} -\/ \mbox{[}options\mbox{]} Send a print job.

{\bfseries{ls}} -\/ \mbox{[}options\mbox{]} List directory contents.

{\bfseries{man}} -\/ \mbox{[}command\mbox{]} Display the help information for the specified command.

{\bfseries{mkdir}} -\/ \mbox{[}options\mbox{]} directory Create a new directory.

{\bfseries{mv}} -\/ \mbox{[}options\mbox{]} source destination Rename or move file(s) or directories.

{\bfseries{passwd}} -\/ \mbox{[}name \mbox{[}password\mbox{]}\mbox{]} Change the password or allow (for the system administrator) to

{\bfseries{change}} -\/ any password.

{\bfseries{ps}} -\/ \mbox{[}options\mbox{]} Display a snapshot of the currently running processes.

{\bfseries{pwd}} -\/ Display the pathname for the current directory.

{\bfseries{rm}} -\/ \mbox{[}options\mbox{]} directory Remove (delete) file(s) and/or directories.

{\bfseries{rmdir}} -\/ \mbox{[}options\mbox{]} directory Delete empty directories.

{\bfseries{ssh}} -\/ \mbox{[}options\mbox{]} user@machine Remotely log in to another Linux machine, over the network.

{\bfseries{Leave}} -\/ an ssh session by typing exit.

{\bfseries{su}} -\/ \mbox{[}options\mbox{]} \mbox{[}user \mbox{[}arguments\mbox{]}\mbox{]} Switch to another user account.

{\bfseries{tail}} -\/ \mbox{[}options\mbox{]} \mbox{[}filename\mbox{]} Display the last n lines of a file (the default is 10).

{\bfseries{tar}} -\/ \mbox{[}options\mbox{]} filename Store and extract files from a tarfile (.tar) or tarball (.tar.\+gz or .tgz).

{\bfseries{top}} -\/ Displays the resources being used on your system. Press q to exit.

{\bfseries{touch}} -\/ filename Create an empty file with the specified name.

{\bfseries{who}} -\/ \mbox{[}options\mbox{]} Display who is logged on. 